Influence of Connectivity on Dung Beetle Communities

### 2025-06-17 corridor_docs/eric_ms_thesis/MS_thesis.Rmd
beuroucracyhowdoyouspellthis

YOUR TITLE GOES HERE 
IN UPPER CASE SINGLE SPACE

@@

YOUR NAME GOES HERE IN ALL CAPITAL LETTERS

@@

© 2025 Your Name Goes Here in Title Case

@@

TITLE OF THE WORK, CENTERED, SINGLE-SPACED,
IN ALL CAPITAL LETTERS, EXACTLY AS ON TITLE PAGE

@@

Your Name as on the Title Page, but in Title Case.

Month and year of graduation

Chair: Name (Do not put Dr. before the name, and do not put degrees after it)  
Cochair: Name (if any, otherwise delete this line)  
Major: See your Editorial Document Management record for your exact major

>>>>

THE INFLUENCE OF CONNECTIVITY ON DUNG BEETLE COMMUNITIES

@@

ERIC ESCOBAR-CHENA

@@

© 2025 Eric Escobar-Chena

@@

THE INFLUENCE OF CONNECTIVITY ON DUNG BEETLE COMMUNITIES

@@

Eric Escobar-Chena

August 2025

Chair: Emilio Bruna  
Major: Wildlife Ecology and Conservation
